### 2019-06-28 thesis-template/msc-thesis.tex
update

\begin{figure}[!t]
\centering
  \begin{minipage}{0.29\textwidth}
  \includegraphics[height=\textwidth]{img/star.png}
    \caption*{\enquote{Star} test field}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.29\textwidth}
    \includegraphics[height=\textwidth]{img/star_ftle.PNG}
     \caption*{LTG slice($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.35\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/star_volume_alt.PNG}
     \caption*{IsoVolume on LTG volume}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{Star} test field}
\label{star_ftle}
\end{figure}
When we look at the example depicted in Fig. \ref{star_ftle}, we can see the FTLE approach LTG responding most in the center of the field, which is the knot point of tensor field lines diverging in any direction. Remark, that there is a light V-shaped ridge on the left on blue background which is outshined by the center spot because of its orders larger magnitude. The volume illustrated on the right even shows a spiked structure for the volume representing all directions at once. The approach detects more ridges in diagonal directions stochastically as we can infer from the Gaussian-shaped plates in the thresholded volume, evenly spaced in $90^\circ$ shifts with $45^\circ$ (quarter volume) offset. These can be interpreted nicely, since the diagonal direction serves a factor $\times\sqrt{2}$ longer mean straight line distance (SLD), leading to $\times\sqrt{2}$ more visited cells on average. The resulting energy distribution will hence be more complete (concerning the occupation of energy in the grid) and hence we will obtain larger differences for our light transport gradient for the diagonal direction, which should be seen gradually and continously as we observe Gaussian-plates in the volume instead of sharp, contrasted ridges. A possible correction would be, to normalize each slice with a factor $\frac{1}{1+(\sqrt{2}-1)\lvert\cos2\omega-\frac{\pi}{4}\rvert}$ to get a uniform response over all directions and account for the longer diagonal run lengths (SLDs). This shows a limitation of the approach, as diagonal ridges are detected predominantly over ridges in axis directions in case both existent, as this test example states. But wouldn't we expect a ridges only in parallel directions? Well, in this case, we could imagine not only tensor field lines diverge or converge, but also they could cross each other unaffectedly (just as with light paths), which could be the case when shifting away from the diagonal directions. For better imagination, offset the light source vertically or horizontally from the diagonals and observe the light paths hitting the axes (which in fact do cross each other).

@@

>>>>

\begin{figure}[!t]
\centering
  \begin{minipage}{0.29\textwidth}
  \includegraphics[height=\textwidth]{img/star.png}
    \caption*{\enquote{Star} test field}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.29\textwidth}
    \includegraphics[height=\textwidth]{img/star_ftle.PNG}
     \caption*{LTG slice($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.35\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/star_volume_alt.PNG}
     \caption*{IsoVolume on LTG volume}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{Star} test field}
\label{star_ftle}
\end{figure}
When we look at the example depicted in Fig. \ref{star_ftle}, we can see the FTLE approach LTG responding most in the center of the field, which is the knot point of tensor field lines diverging in any direction. Remark, that there is a light V-shaped ridge on the left on blue background which is outshined by the center spot because of its orders larger magnitude. The volume illustrated on the right even shows a spiked structure for the volume representing all directions at once. The approach detects more ridges in diagonal directions stochastically as we can infer from the Gaussian-shaped plates in the thresholded volume, evenly spaced in $90^\circ$ shifts with $45^\circ$ (quarter volume) offset. These can be interpreted nicely, since the diagonal direction serves a factor $\times\sqrt{2}$ longer mean straight line distance (SLD), leading to $\times\sqrt{2}$ longer ridges. The resulting energy distribution will hence be more complete (concerning the occupation of energy in the grid) and hence we will obtain larger differences for our light transport gradient for the diagonal direction, which should be seen gradually and continously as we observe Gaussian-plates in the volume instead of sharp, contrasted ridges. But wouldn't we expect a ridges only in parallel directions? Well, in this case, we could imagine not only tensor field lines diverge or converge, but also they could cross each other unaffectedly (just as with light paths), which could be the case when shifting away from the diagonal directions. For better imagination, offset the light source vertically or horizontally from the diagonals and observe the light paths hitting the axes (which in fact do cross each other).

%A possible correction would be, to normalize each slice with a heuristic factor $\frac{1}{1+(\sqrt{2}-1)\lvert\cos2\omega-\frac{\pi}{4}\rvert}$ to get a uniform response over all directions and account for the longer diagonal run lengths (SLDs).

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/slice16.png}
    \caption*{$\mathop{res}=29\times29\times16$}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/slice32.PNG}
     \caption*{$\mathop{res}=51\times51\times16$}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/slice64.PNG}
     \caption*{$\mathop{res}=101\times101\times16$}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{inverse} test field - slice}
\label{resA_ftle}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
 	\centering
  \includegraphics[height=\textwidth]{img/vol16.png}
    \caption*{$\mathop{res}=29\times29\times16$}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/vol32.PNG}
     \caption*{$\mathop{res}=51\times51\times16$}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/vol64.PNG}
     \caption*{$\mathop{res}=101\times101\times16$}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{inverse} test field - volume}
\label{resA_ftle_volume}
\end{figure}
